---
title: CRAN Usage
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

<details>

<summary>Get and read the log - show/hide code</summary>

```{r get_log}
yesterday <- Sys.Date() - 1
year <- format(Sys.Date() - 1, "%Y")
url <- paste0("http://cran-logs.rstudio.com/", year, "/", yesterday, ".csv.gz")
filename <- paste0(yesterday, ".csv.gz")
if (!file.exists(filename)) {
  cat(paste0("Downloading: ", filename))
  download.file(url, destfile = filename)
}
cranlog <- read.csv(gzfile(filename))
```

</details>

### Yesterday (`r yesterday`), there were `r format(length(cranlog$ip_id), big.mark=",")` distinct package downloads and `r format(length(unique(cranlog$ip_id)), big.mark=",")` unique users on cran.rstudio.com.

---

# By R version

```{r r_version, fig.width=10}
barplot(table(cranlog$r_version), las = 2, cex.names = 1.3)
```

# By OS

```{r by_os, fig.width=10}
r_os_macos <- gsub("^darwin.*", "MacOS", cranlog$r_os)
r_os <- gsub("mingw32", "Windows", r_os_macos)
barplot(table(r_os))
```

# By Architecture

```{r by_arch, fig.width=10}
barplot(table(cranlog$r_arch), cex.names = .8)
```

# By Country

Uses two letter ISO country code.

US downloads of `r table(cranlog$country[cranlog$country == "US"])`, dwarf other countries and are therefore excluded from the chart for clarity. We also drop all the countries with less than 10,000 downloads.

```{r by_country, fig.width=10}
country_data <- table(cranlog$country[cranlog$country != "US"])
barplot(country_data[country_data > 10000], las = 2, cex.names = .9)
```
Or if you'd prefer a straight up top 20, here it is:

```{r country_top20}
head(sort(table(cranlog$country), decreasing = T), 20)
```

Another half-baked [sellorm](https://twitter.com/sellorm) rough cut.
